\plaintitle

### 2025-03-13 docs/style/article-body.tex
stashing...

In order to evaluate just how much constraint our implementation can allow, our aim is to try our implementation on other MCUs with varying levels of power and hardware support. Whereas Teensy 4.1 is our primary development platform, we aim to run our implementations on Raspberry Pi Pico 2\footnote{\href{https://datasheets.raspberrypi.com/pico/pico-2-product-brief.pdf}{Raspberry Pi Pico 2 documentation, accessed 2025-03-13}} as well as ESP32-S3\footnote{\href{https://www.espressif.com/sites/default/files/documentation/esp32-s3_datasheet_en.pdf}{ESP32-S3 documentation, accessed 2025-03-13}}. Due to the lower computational power of these MCUs, there may be significant issues in utilizing these weaker models, yet they are significantly cheaper and easier to access.

@@

As mentioned in section 3.4, Chouhan et al. \cite{toeplitz-desc} utilized FPGA to implement Toeplitz extraction specifically for OQRNG, a work also studied by Zhang et al. \cite{zhang}. Furthermore, Zhang et al.~utilized a standardized min-entropy evaluation to ensure true, unbiased randomness in their result. Both of these implementations utilize powerful hardware where the matrix multiplication is offloaded to FPGA. These implementations provided extraction speeds of between 3.36 Gpbs \cite{zhang} to 26.57 Gbps \cite{toeplitz-desc}. Neither of these implementations operate on constrained hardware, instead creating bespoke circuit boards for their works.

>>>>

In order to evaluate just how much constraint our implementation can allow, our aim is to try our implementation on other MCUs with varying levels of power and hardware support. Whereas Teensy 4.1 is our primary development platform which we will evaluate closely, we aim to run our implementations on Raspberry Pi Pico 2\footnote{\href{https://datasheets.raspberrypi.com/pico/pico-2-product-brief.pdf}{Raspberry Pi Pico 2 documentation, accessed 2025-03-13}} as well as ESP32-S3\footnote{\href{https://www.espressif.com/sites/default/files/documentation/esp32-s3_datasheet_en.pdf}{ESP32-S3 documentation, accessed 2025-03-13}}. Due to the lower computational power of these MCUs, there may be significant issues in utilizing these weaker models, yet they are significantly cheaper and easier to access. Testing of these will consist solely of running the implementation on these controllers and measuring execution speed.

@@

As mentioned in section 3.4, Chouhan et al. \cite{toeplitz-desc} utilized FPGA to implement Toeplitz extraction specifically for OQRNG, a work also studied by Zhang et al. \cite{toeplitz}. Furthermore, Zhang et al.~utilized a standardized min-entropy evaluation to ensure true, unbiased randomness in their result. Both of these implementations utilize powerful hardware where the matrix multiplication is offloaded to FPGA. These implementations provided extraction speeds of between 3.36 Gpbs \cite{toeplitz} to 26.57 Gbps \cite{toeplitz-desc}. Neither of these implementations operate on constrained hardware, instead creating bespoke circuit boards for their works.
